Blum axioms and nondeterministic computation of functions

### 2016-04-12 paper.tex
paper.tex: Add citation about Turing machines never writing 0 over 1.

    And, as an off-line Turing machine
    (a machine with a special read-only tape for its input)
    can simulate any Turing machine without ever writing a $0$ over a $1$,
    we can associate an encoding of a off-line Turing machine
    with the function that counts the number of times
    it writes a $0$ over an $1$ before halting
    (the number can be converted to binary and have its most significant digit removed
    to generate all possible binary strings).
    (The machine can choose how many times it will write a $0$ over an $1$,
    thus we can generate any partial recursive function by manipulating this choice.)
\end{example}

>>>>

    And, as an off-line Turing machine
    (a machine with a special read-only tape for its input)
    can simulate any Turing machine without ever writing a $0$ over a~$1$
    \cite[p.~174]{HopcroftUllman1979},
    we can associate an encoding of a off-line Turing machine
    with the function that counts the number of times
    it writes a $0$ over an $1$ before halting
    (the number can be converted to binary and have its most significant digit removed
    to generate all possible binary strings).
    (The machine can choose how many times it will write a $0$ over an $1$,
    thus we can generate any partial recursive function by manipulating this choice.)
\end{example}
